---
output: _output.yaml
---

## {data-background="images/import.png"}

## Agenda

<hr>

- read data from flat or delimited files
- read data from excel spreadsheets
- read data from other statistical softwares
- specify column/variable types
- read specific columns/variables 

## Libraries

<hr>

```{r importlib1,eval=FALSE}
library(readr)
library(readxl)
library(haven)
```

```{r importlib2, echo=FALSE, eval=TRUE, results='hide', message=FALSE}
library(readr)
library(readxl)
library(haven)
```

## {data-background="images/csv_file.png"}

## {data-background="images/semi_colon_file.png"}

## {data-background="images/space_file.png"}

## {data-background="images/tab_file.png"}

## CSV 

<hr>

```{r import2, echo=TRUE, results='markup', message=FALSE}
read_csv('data/mtcars.csv')
```

## CSV 

<hr>

```{r import2a, echo=TRUE, results='markup', message=FALSE}
read_delim('data/mtcars.csv', delim = ",")
```

## {data-background="images/columns_names.png"}

## Column Names 

<hr>

```{r import4a, echo=TRUE, results='markup', message=FALSE}
read_csv('data/mtcars1.csv')
```

## Column Names 

<hr>

```{r import4, echo=TRUE, results='markup', message=FALSE}
read_csv('data/mtcars1.csv', col_names = FALSE)
```

## {data-background="images/mtcars_skip_lines_file.png"}

## Skip Lines 

<hr>

```{r import6a, echo=TRUE, results='markup', message=FALSE}
read_csv('data/mtcars2.csv')
```

## Skip Lines 

<hr>

```{r import6, echo=TRUE, results='markup', message=FALSE}
read_csv('data/mtcars2.csv', skip = 19)
```

## Maximum Lines 

<hr>

```{r import8, echo=TRUE, results='markup', message=FALSE}
read_csv('data/mtcars.csv', n_max = 20)
```

## {data-background="images/column_types_list_canva.png"}

## Column Types

<hr>

```{r import55, echo=TRUE, results='markup', message=FALSE}
spec_csv('data/mtcars5.csv')
```

## {data-background="images/column_objective_canva.png"}

## Column Types 

<hr>

```{r import10, echo=TRUE, results='markup', message=FALSE}
read_csv('data/mtcars5.csv', 
         col_types = list(col_double(), col_factor(levels = c(4, 6, 8)),
                          col_double(), col_integer()))
```

## Skip Columns

<hr>

```{r import10a, echo=TRUE, results='markup', message=FALSE}
read_csv('data/mtcars5.csv', 
         col_types = list(col_double(), col_factor(levels = c(4, 6, 8)),
                          col_skip(), col_integer()))
```


## Read Specific Columns 

<hr>

```{r import11, echo=TRUE, results='markup', message=FALSE}
read_csv('data/mtcars5.csv', 
         col_types = cols_only(mpg = col_double(), 
                               cyl = col_factor(levels = c(4, 6, 8))))
```

## {data-background="images/import_funcs.png"}

## Your turn...

<hr>

Open the below files, examine how the values are separated and read them into R
using the appropriate function listed in the previous slide:

- mtcars.txt
- mtcars.tsv
- mtcars3.txt
- mtcars4.txt

## Spreadsheets

<hr>

- list sheets in an excel file
- read data from an excel sheet
- read specific cells
- read specific rows
- read specific columns

## List Sheets

<hr>

```{r import55a}
excel_sheets('data/sample.xls')
```

## Read Sheet

<hr>

```{r import56, echo=TRUE, results='markup', message=FALSE}
read_excel('data/sample.xls', sheet = 1)
```

## {data-background="images/readxl_range_canva.png"}

## Read Specific Cells

<hr>

```{r import58, echo=TRUE, results='markup', message=FALSE}
read_excel('data/sample.xls', sheet = 1, range = "B1:C4")
```

## Read Single Column

<hr>

```{r import64, echo=TRUE, results='markup', message=FALSE}
readxl::read_excel('data/sample.xls', sheet = 1, range = cell_cols(2))
```


## Specific Rows

<hr>

```{r import62, echo=TRUE, results='markup', message=FALSE}
readxl::read_excel('data/sample.xls', sheet = 1, range = cell_rows(1:4))
```

## Specific Columns

<hr>

```{r import63, echo=TRUE, results='markup', message=FALSE}
readxl::read_excel('data/sample.xls', sheet = 1, range = cell_cols(2:3))
```


## Statistical Softwares

<hr>

- SAS
- SPSS
- STATA

## STATA

<hr>

```{r import68, echo=TRUE, results='markup', message=FALSE}
haven::read_stata('data/airline.dta')  
```

## SPSS

<hr>

```{r import71, echo=TRUE, results='markup', message=FALSE}
read_spss('data/employee.sav')  
```

## SAS

<hr>

```{r import73, echo=TRUE, results='markup', message=FALSE}
read_sas('data/airline.sas7bdat')
```

## {data-background="images/readxl_functions_summary_canva.png"}


## {data-background="images/thankyou.png"}

