---
title: "Introduction"
author: "Aravind Hebbali"
date: "16 April 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## DSCE Business Analytics Conclave Workshop

19th, 20th & 21st April, 2pm - 5pm

## Introduction

Materials for the workshop. Please install all the required softwares and
download the data sets and scripts from this repository before the
workshop. 

## Software Prerequisites

### R

R can be installed from the R project [website](https://cran.r-project.org/).
Please install the latest version 3.4.4. 

### RStudio

RStudio IDE can be installed from the RStudio [website](https://www.rstudio.com/products/rstudio/download/). Install the free
desktopo version.

### R Packages

Below are a list of R packages required for the workshop. 

- readr
- readxl
- haven
- dplyr
- ggplot2
- magrittr
- descriptr
- skimr
- inferr
- olsrr
- blorr
- rmarkdown
- knitr
- devtools
- blorr
- caret

You can install the packages by running the following code in R:

```{r install, eval=FALSE}
install.packages("package_name")
```

### Anaconda

Download and install the Anaconda distribution from their [website](https://www.anaconda.com/download/). We will use [Jupyter Notebook](http://jupyter.org/) for the python session.

## R Session

- Quick tour of R & RStudio
- Importing data into R
- Data Wrangling
- Data Visualization
- Exploratory Data Analysis
- Linear Regression
- Logistic Regression

## Python Session

- Data Wrangling with Pandas
- Data Visualization 
    - matplotlib
    - bokeh
    - plotly
- Modeling with statsmodels

## Useful Resources

- [Rstudio Webinars](https://www.rstudio.com/resources/webinars/)
- [RStudio Cheat Sheets](https://www.rstudio.com/resources/cheatsheets/)
- [tidyverse](https://www.tidyverse.org/)
- [R Bloggers](https://www.r-bloggers.com/)
- [R Weekly](https://rweekly.org/)

