---
output: _output.yaml
---

## {data-background="images/gg_intro.png"}

## Agenda

<hr>

- explore graphics systems in R
- understand grammar of graphics
- understand geoms
- explore aesthetics to modify geoms
- use facets for sub plots
- change coordinate system

## Why visualize data?

<hr>

- explore and explain patterns and trends
- detect anomalies in data
- make sense of large amount of data efficiently and in time
- easy to communicate and share insights from data


## Graphics Systems 

<hr>

- Base R
- ggplot2
- lattice

## Libraries

<hr>

```{r libs, echo=TRUE, eval=TRUE, results='hide', message=FALSE}
library(ggplot2)
library(readr)
library(descriptr)
library(gridExtra)
```

## Grammar of Graphics

<hr>

Grammar of graphics is a formal system for building plots. The core idea is that any plot can be uniquely described as a combination of

- a dataset
- a geom
- a set of mappings
- a statistic
- a position adjustment
- a coordinate system
- a faceting scheme


## Coordinate System

<hr>

```{r gg1, fig.align='center'}
ggplot()
```

## Data Set

<hr>

```{r gg2, fig.align='center'}
ggplot(data = mtcarz)
```

## Geoms

<hr>

```{r gg3, fig.align='center'}
ggplot(data = mtcarz) + 
  geom_point(mapping = aes(x = disp, y = mpg))
```

## Geoms

<hr>

```{r gg4, fig.align='center'}
ggplot(data = mtcarz) +
  geom_histogram(mapping = aes(x = mpg))
```

## Geoms

<hr>

```{r gg5, fig.align='center'}
ggplot(data = mtcarz) +
  geom_boxplot(mapping = aes(x = cyl, y = mpg))
```

## Geoms

<hr>

```{r gg6, fig.align='center'}
ggplot(data = mtcarz) +
  geom_bar(mapping = aes(x = cyl))
```

## Aesthetics

<hr>

- color
- shape
- size
- background color
- transparency
- line type

## Color

<hr>

```{r gg37, echo=FALSE, fig.align='center'}
p1 <- ggplot(data = mtcarz) + 
  geom_point(mapping = aes(x = disp, y = mpg), color = "blue")
p2 <- ggplot(data = mtcarz) + 
  geom_point(mapping = aes(x = disp, y = mpg), color = "red")
grid.arrange(p1, p2, ncol = 2)
```

## Color Hex Code

<hr>

```{r gg43, fig.align='center'}
ggplot(data = mtcarz) + 
  geom_point(mapping = aes(x = disp, y = mpg), color = "#0000ff")
```

## {data-background="images/ggplot2_palette_canva.png"}

## Color Palette

<hr>

```{r gg44, fig.align='center'}
ggplot(mtcarz) +
  geom_bar(aes(x = cyl), fill = rainbow(3))
```

## {data-background="images/ggplot2_shape_canva.png"}

## Shape

<hr>

```{r gg38, echo=FALSE, fig.align='center'}
p1 <- ggplot(data = mtcarz) + 
  geom_point(mapping = aes(x = disp, y = mpg), shape = 5)
p2 <- ggplot(data = mtcarz) + 
  geom_point(mapping = aes(x = disp, y = mpg), color = 22)
grid.arrange(p1, p2, ncol = 2)
```

## Size

<hr>

```{r gg39, echo=FALSE, fig.align='center'}
p1 <- ggplot(data = mtcarz) + 
  geom_point(mapping = aes(x = disp, y = mpg), size = 1)
p2 <- ggplot(data = mtcarz) + 
  geom_point(mapping = aes(x = disp, y = mpg), size = 2)
grid.arrange(p1, p2, ncol = 2)
```

## Background Color

<hr>

```{r gg40, echo=FALSE, fig.align='center'}
p1 <- ggplot(data = mtcarz) + geom_bar(mapping = aes(x = cyl), fill = "blue")
p2 <- ggplot(data = mtcarz) + geom_bar(mapping = aes(x = cyl), fill = "red")
grid.arrange(p1, p2, ncol = 2)
```

## Transparency

<hr>

```{r gg47, echo=FALSE, fig.align='center'}
p1 <- ggplot(data = mtcarz) + geom_bar(mapping = aes(x = cyl), 
                                       fill = "red", alpha = 0.5)
p2 <- ggplot(data = mtcarz) + geom_bar(mapping = aes(x = cyl), 
                                       fill = "red", alpha = 0.95)
grid.arrange(p1, p2, ncol = 2)
```

## Map Color

<hr>

```{r gg7, fig.align='center'}
ggplot(data = mtcarz) + 
  geom_point(aes(x = disp, y = mpg, color = cyl))
```

## Map Shape

<hr>

```{r gg8, fig.align='center'}
ggplot(data = mtcarz) + 
  geom_point(aes(x = disp, y = mpg, shape = factor(gear)))
```

## Map Size

<hr>

```{r gg9, fig.align='center'}
ggplot(data = mtcarz) + 
  geom_point(aes(x = disp, y = mpg, size = wt))
```

## Color = blue

<hr>

```{r gg10, fig.align='center'}
ggplot(data = mtcarz) + 
  geom_point(aes(x = disp, y = mpg), color = "blue")
```

## Shape = 3

<hr>

```{r gg11, fig.align='center'}
ggplot(data = mtcarz) + 
  geom_point(aes(x = disp, y = mpg), shape = 3)
```

## Size = 2

<hr>

```{r gg12, fig.align='center'}
ggplot(data = mtcarz) + 
  geom_point(aes(x = disp, y = mpg), size = 2)
```

## {data-background="images/ggplot2_transform_canva.png"}

## Bar chart

<hr>

```{r gg13, fig.align='center'}
ggplot(data = mtcarz) +
  stat_count(mapping = aes(x = cyl))
```

## Histograms

<hr>

```{r gg41, fig.align='center'}
ggplot(data = mtcarz) +
  stat_bin(mapping = aes(x = mpg))
```

## Box plots

<hr>

```{r gg42, fig.align='center'}
ggplot(data = mtcarz) +
  stat_boxplot(mapping = aes(x = cyl, y = mpg))
```

## Position

<hr>

```{r gg14, fig.align='center'}
ggplot(data = mtcarz) +
  geom_bar(mapping = aes(x = cyl, fill = gear))
```

## Position

<hr>

```{r gg15, fig.align='center'}
ggplot(data = mtcarz) +
  geom_bar(mapping = aes(x = cyl, fill = gear), position = "dodge")
```

## Flip Coordinates

<hr>

```{r gg16, fig.align='center'}
ggplot(data = mtcarz) +
  geom_bar(mapping = aes(x = cyl, fill = gear)) +
  coord_flip()
```

## Facets

<hr>

- split the plot into sub plots 
- each subplot displays a subset of the data
- use `facet_wrap()` to create sub plots based on a single variable
- use `facet_grid()` to create sub plots based on a two variable

## Facets

<hr>

```{r gg17, fig.align='center'}
ggplot(data = mtcarz) +
  geom_point(mapping = aes(x = disp, y = mpg)) +
  facet_wrap(~ cyl)
```

## Facets

<hr>

```{r gg18, fig.align='center'}
ggplot(data = mtcarz) +
  geom_point(mapping = aes(x = disp, y = mpg)) +
  facet_grid(gear ~ cyl)
```

## Facets

<hr>

```{r gg35, fig.align='center'}
ggplot(data = mtcarz) +
  geom_point(mapping = aes(x = disp, y = mpg)) +
  facet_grid(cyl ~ gear)
```

## Title, Axis Labels & Limits

<hr>

```{r gg19, fig.align='center'}
ggplot(data = mtcarz) + 
  geom_point(aes(x = disp, y = mpg), color = "blue") +
  labs(title = "mpg vs disp", x = "Displacement", 
       y = "Miles Per Gallon")
```

## Title

<hr>

```{r gg20, fig.align='center'}
ggplot(data = mtcarz) + 
  geom_point(aes(x = disp, y = mpg), color = "blue") +
  ggtitle("mpg vs disp") + xlab("Displacement") + 
  ylab("Miles Per Gallon")
```

## Axis Limits

<hr>

```{r gg21, fig.align='center'}
ggplot(data = mtcarz) +
  geom_point(aes(x = disp, y = mpg), color = "blue") +
  xlim(c(0, 600))
```

## Axis Limits

<hr>

```{r gg22, fig.align='center'}
ggplot(data = mtcarz) +
  geom_point(aes(x = disp, y = mpg), color = "blue") +
  ylim(c(0, 40))
```

## Axis Limits

<hr>

```{r gg23, fig.align='center'}
ggplot(data = mtcarz) +
  geom_point(aes(x = disp, y = mpg), color = "blue") +
  expand_limits(x = c(0, 600), y = c(0, 40))
```

## Line Chart: Data

<hr>

```{r gg24, echo=TRUE, message=FALSE}
device <- read_csv("data/users_device.csv",
                   col_types = list(col_date(format = "%m/%d/%y"),
                                    col_integer(), col_integer(),
                                    col_integer()))
device
```

## Line Chart

<hr>

```{r gg25, fig.align='center'}
ggplot(data = device) +
  geom_line(mapping = aes(x = Date, y = Desktop))
```

## Line Color

<hr>

```{r gg26, fig.align='center'}
ggplot(data = device) +
  geom_line(mapping = aes(x = Date, y = Desktop), color = "blue")
```

## Line Type

<hr>

```{r gg27, fig.align='center'}
ggplot(data = device) +
  geom_line(mapping = aes(x = Date, y = Desktop), linetype = 2)
```

## Line Type

<hr>

```{r gg28, fig.align='center'}
ggplot(data = device) +
  geom_line(mapping = aes(x = Date, y = Desktop), linetype = "dashed")
```

## Line Width

<hr>

```{r gg29, fig.align='center'}
ggplot(data = device) +
  geom_line(mapping = aes(x = Date, y = Desktop), size = 2)
```

## Multiple Lines

<hr>

```{r gg30, fig.align='center'}
ggplot(data = device) +
  geom_line(mapping = aes(x = Date, y = Desktop)) +
  geom_line(mapping = aes(x = Date, y = Mobile))
```

## Multiple Lines

<hr>

```{r gg31, fig.align='center'}
ggplot(data = device) +
  geom_line(mapping = aes(x = Date, y = Desktop)) +
  geom_line(mapping = aes(x = Date, y = Mobile)) +
  geom_line(mapping = aes(x = Date, y = Tablet))
```

## Multiple Lines

<hr>

```{r gg45, fig.align='center'}
ggplot(data = device) +
  geom_line(mapping = aes(x = Date, y = Desktop), linetype = 2) +
  geom_line(mapping = aes(x = Date, y = Mobile), linetype = 3) +
  geom_line(mapping = aes(x = Date, y = Tablet), linetype = 4)
```

## Line Chart: Data

<hr>

```{r gg32, echo=TRUE, message=FALSE}
tidy_device <- read_csv("data/tidy_users.csv",
                        col_types = list(col_date(format = "%m/%d/%y"),
                                         col_character(), col_integer()))
tidy_device
```

## Multiple Lines

<hr>

```{r gg33, fig.align='center'}
ggplot(data = tidy_device) +
  geom_line(mapping = aes(x = Date, y = Users, group = Device, 
                          color = Device))
```

## Multiple Lines

<hr>

```{r gg34, fig.align='center'}
ggplot(data = tidy_device) +
  geom_line(mapping = aes(x = Date, y = Users, group = Device, 
                          linetype = Device))
```


## {data-background="images/thankyou.png"}