---
output: _output.yaml
---

## {data-background="images/gg_intro.png"}

## Agenda

<hr>

## Libraries

<hr>

```{r dplyr1, eval=FALSE}
library(ggplot2)
library(readr)
library(descriptr)
```

```{r libs, echo=FALSE, eval=TRUE, results='hide', message=FALSE}
library(ggplot2)
library(readr)
library(descriptr)
```

## Coordinate System

<hr>

```{r gg1, fig.align='center'}
ggplot()
```

## Data Set

<hr>

```{r gg2, fig.align='center'}
ggplot(data = mtcarz)
```

## Geoms

<hr>

<!-- ## represent relationship using points
## map variables in the data to visual properties
## x axis represents vehicle displacement
## y axis represents mileage
 -->
```{r gg3, fig.align='center'}
ggplot(data = mtcarz) + 
  geom_point(mapping = aes(x = disp, y = mpg))
```

## Geoms

<hr>

```{r gg4, fig.align='center'}
ggplot(data = mtcarz) +
  geom_histogram(mapping = aes(x = mpg))
```

## Geoms

<hr>

```{r gg5, fig.align='center'}
ggplot(data = mtcarz) +
  geom_boxplot(mapping = aes(x = cyl, y = mpg))
```

## Geoms

<hr>

```{r gg6, fig.align='center'}
ggplot(data = mtcarz) +
  geom_bar(mapping = aes(x = cyl))
```

## Aesthetics

<hr>

## Color

<hr>

## Shape

<hr>

## Size

<hr>

## Background Color

<hr>

## Transparency

<hr>

## Map Color

<hr>

```{r gg7, fig.align='center'}
ggplot(data = mtcarz) + 
  geom_point(aes(x = disp, y = mpg, color = cyl))
```

## Map Shape

<hr>

```{r gg8, fig.align='center'}
ggplot(data = mtcarz) + 
  geom_point(aes(x = disp, y = mpg, shape = factor(gear)))
```

## Map Size

<hr>

```{r gg9, fig.align='center'}
ggplot(data = mtcarz) + 
  geom_point(aes(x = disp, y = mpg, size = wt))
```

<hr>

## Color = blue

<hr>

```{r gg10, fig.align='center'}
ggplot(data = mtcarz) + 
  geom_point(aes(x = disp, y = mpg), color = "blue")
```

## Shape = 3

<hr>

```{r gg11, fig.align='center'}
ggplot(data = mtcarz) + 
  geom_point(aes(x = disp, y = mpg), shape = 3)
```

## Size = 2

<hr>

```{r gg12, fig.align='center'}
ggplot(data = mtcarz) + 
  geom_point(aes(x = disp, y = mpg), size = 2)
```

## Transformations

<hr>

## Bar chart

<hr>

```{r gg13, fig.align='center'}
ggplot(data = mtcarz) +
  stat_count(mapping = aes(x = cyl))
```

## Histograms

<hr>

## Box plots

<hr>

## Position

<hr>

```{r gg14, fig.align='center'}
ggplot(data = mtcarz) +
  geom_bar(mapping = aes(x = cyl, fill = factor(gear)))
```

## Position

<hr>

```{r gg15, fig.align='center'}
ggplot(data = mtcarz) +
  geom_bar(mapping = aes(x = cyl, fill = factor(gear)), position = "dodge")
```

## Flip Coordinates

<hr>

```{r gg16, fig.align='center'}
ggplot(data = mtcarz) +
  geom_bar(mapping = aes(x = cyl, fill = factor(gear))) +
  coord_flip()
```

## Facets

<hr>

- split the plot into sub plots each of which 
- displays a subset of the data
- examine the relationship between disp and mpg for cyl

## Facets

<hr>

```{r gg17, fig.align='center'}
ggplot(data = mtcarz) +
  geom_point(mapping = aes(x = disp, y = mpg)) +
  facet_wrap(~ cyl)
```

## Facets

<hr>

```{r gg18, fig.align='center'}
ggplot(data = mtcarz) +
  geom_point(mapping = aes(x = disp, y = mpg)) +
  facet_grid(gear ~ cyl)
```

## Title, Axis Labels & Limits

<hr>

```{r gg19, fig.align='center'}
ggplot(data = mtcarz) + 
  geom_point(aes(x = disp, y = mpg), color = "blue") +
  labs(title = "mpg vs disp", x = "Displacement", y = "Miles Per Gallon")
```

## Title

<hr>

```{r gg20, fig.align='center'}
ggplot(data = mtcarz) + 
  geom_point(aes(x = disp, y = mpg), color = "blue") +
  ggtitle("mpg vs disp") + xlab("Displacement") + ylab("Miles Per Gallon")
```

## Axis Limits

<hr>

```{r gg21, fig.align='center'}
ggplot(data = mtcarz) +
  geom_point(aes(x = disp, y = mpg), color = "blue") +
  xlim(c(0, 600))
```

## Axis Limits

<hr>

```{r gg22, fig.align='center'}
ggplot(data = mtcarz) +
  geom_point(aes(x = disp, y = mpg), color = "blue") +
  ylim(c(0, 40))
```

## Axis Limits

<hr>

```{r gg23, fig.align='center'}
ggplot(data = mtcarz) +
  geom_point(aes(x = disp, y = mpg), color = "blue") +
  expand_limits(x = c(0, 600), y = c(0, 40))
```

## Line Chart: Data

<hr>

```{r gg24, echo=FALSE, message=FALSE}
device <- read_csv("data/users_device.csv",
                   col_types = list(col_date(format = "%m/%d/%y"),
                                    col_integer(), col_integer(),
                                    col_integer()))
```

## Line Chart

<hr>

```{r gg25, fig.align='center'}
ggplot(data = device) +
  geom_line(mapping = aes(x = Date, y = Desktop))
```

## Line Color

<hr>

```{r gg26, fig.align='center'}
ggplot(data = device) +
  geom_line(mapping = aes(x = Date, y = Desktop), color = "blue")
```

## Line Type

<hr>

```{r gg27, fig.align='center'}
ggplot(data = device) +
  geom_line(mapping = aes(x = Date, y = Desktop), linetype = 2)
```

## Line Type

<hr>

```{r gg28, fig.align='center'}
ggplot(data = device) +
  geom_line(mapping = aes(x = Date, y = Desktop), linetype = "dashed")
```

## Line Width

<hr>

```{r gg29, fig.align='center'}
ggplot(data = device) +
  geom_line(mapping = aes(x = Date, y = Desktop), size = 2)
```

## Multiple Lines

<hr>

```{r gg30, fig.align='center'}
ggplot(data = device) +
  geom_line(mapping = aes(x = Date, y = Desktop)) +
  geom_line(mapping = aes(x = Date, y = Mobile))
```

## Multiple Lines

<hr>

```{r gg31, fig.align='center'}
ggplot(data = device) +
  geom_line(mapping = aes(x = Date, y = Desktop)) +
  geom_line(mapping = aes(x = Date, y = Mobile)) +
  geom_line(mapping = aes(x = Date, y = Tablet))
```

## Line Chart: Data

<hr>

```{r gg32, echo=FALSE, message=FALSE}
tidy_device <- read_csv("data/tidy_users.csv",
                        col_types = list(col_date(format = "%m/%d/%y"),
                                         col_character(), col_integer()))
```

## Multiple Lines

<hr>

```{r gg33, fig.align='center'}
ggplot(data = tidy_device) +
  geom_line(mapping = aes(x = Date, y = Users, group = Device, color = Device))
```


#### {data-background="images/thankyou.png"}