---
output: _output.yaml
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Agenda

<hr>

- generate descriptive statistics for
    - continuous data
    - categorical data
- use visualization to explore data

## Libraries

<hr>

```{r eda1, eval=TRUE, echo=TRUE, message=FALSE, results='hide'}
library(skimr)
library(descriptr)
```

## Data Screening

<hr>

```{r eda0}
ds_screener(mtcarz)
```

## Summary Statistics

<hr>

```{r eda2}
summary(mtcarz)
```

## Summary Statistics

<hr>

```{r eda3}
skim(mtcarz)
```

## Continuous Data

<hr>

```{r eda4}
ds_summary_stats(mtcarz, mpg)
```

## Continuous Data

<hr>

```{r eda4a}
ds_multi_stats(mtcarz, mpg, disp, hp)
```

## Continuous Data

<hr>

```{r eda6a, fig.align='center', fig.width=4, fig.height=3}
plot(ds_freq_cont(mtcarz, mpg))
```

## Categorical Data

<hr>

```{r eda7}
ds_freq_table(mtcarz, cyl)
```

## Categorical Data

<hr>

```{r eda8, fig.align='center'}
k <- ds_freq_table(mtcarz, cyl)
plot(k)
```

## Categorical Data

<hr>

```{r eda9}
ds_cross_table(mtcarz, cyl, gear)
```

## Categorical Data

<hr>

```{r eda10, fig.align='center'}
k <- ds_cross_table(mtcarz, cyl, gear)
plot(k)
```

## Categorical Data

<hr>

```{r eda11, fig.align='center'}
k <- ds_cross_table(mtcarz, cyl, gear)
plot(k, stacked = TRUE)
```

## Categorical Data

<hr>

```{r eda12, fig.align='center'}
k <- ds_cross_table(mtcarz, cyl, gear)
plot(k, proportional = TRUE)
```

## Grouped Summaries

<hr>

```{r eda13}
ds_group_summary(mtcarz, cyl, mpg)
```

## Grouped Summaries

<hr>

```{r eda14, fig.align='center'}
k <- ds_group_summary(mtcarz, cyl, mpg)
plot(k)
```
