---
output: _output.yaml
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Agenda

<hr>

## Libraries

<hr>

```{r lm1, message=FALSE, results='hide'}
library(readxl)
library(caret)
library(olsrr)
```


## Data

<hr>

```{r lm2}
housing <- read_excel("data/boston.xls")
housing
```

## Data Partition

<hr>

```{r lm3}
out <- createDataPartition(y = housing$CRIM, p = 0.7, list = FALSE)
train <- housing[out, ]
test <- housing[-out, ]
```

## Regression

<hr>

```{r lm4}
model <- lm(MV ~ ., data = housing)
model
```

## Regression

<hr>

```{r lm5}
model <- lm(MV ~ ., data = housing)
summary(model)
```

## Regression

<hr>

```{r lm6}
model <- lm(MV ~ ., data = housing)
ols_regress(model)
```

## Stepwise Regression

<hr>

```{r lm7}
model <- lm(MV ~ ., data = housing)
ols_step_forward_aic(model)
```

## Stepwise Regression

<hr>

```{r lm8}
model <- lm(MV ~ ., data = housing)
ols_step_backward_aic(model)
```

## Stepwise Regression

<hr>

```{r lm9}
model <- lm(MV ~ ., data = housing)
ols_step_both_aic(model)
```

## Residual Diagnostics

<hr>

```{r lm10, fig.align='center'}
model <- lm(MV ~ ., data = housing)
ols_plot_resid_qq(model)
```

## Residual Diagnostics

<hr>

```{r lm11}
model <- lm(MV ~ ., data = housing)
ols_test_normality(model)
```

## Residual Diagnostics

<hr>

```{r lm12, fig.align='center'}
model <- lm(MV ~ ., data = housing)
ols_plot_resid_fit(model)
```

## Residual Diagnostics

<hr>

```{r lm13, fig.align='center'}
model <- lm(MV ~ ., data = housing)
ols_plot_resid_hist(model)
```

## Collinearity Diagnostics

<hr>

```{r lm14}
model <- lm(MV ~ ., data = housing)
ols_coll_diag(model)
```

## Part & Partial Correlations

<hr>

```{r lm15}
model <- lm(MV ~ ., data = housing)
ols_correlations(model)
```

## Heteroskedasticity

<hr>

```{r lm16}
model <- lm(MV ~ ., data = housing)
ols_test_breusch_pagan(model)
```


## Heteroskedasticity

<hr>

```{r lm17}
model <- lm(MV ~ ., data = housing)
ols_test_score(model)
```


## Heteroskedasticity

<hr>

```{r lm18}
model <- lm(MV ~ ., data = housing)
ols_test_f(model)
```

## Measures of Influence

<hr>

```{r lm19, fig.align='center'}
model <- lm(MV ~ ., data = housing)
ols_plot_cooksd_bar(model)
```

## Measures of Influence

<hr>

```{r lm20, fig.align='center'}
model <- lm(MV ~ ., data = housing)
ols_plot_dffits(model)
```

## Measures of Influence

<hr>

```{r lm21, fig.align='center'}
model <- lm(MV ~ ., data = housing)
ols_plot_resid_stand(model)
```

## Measures of Influence

<hr>

```{r lm22, fig.align='center'}
model <- lm(MV ~ ., data = housing)
ols_plot_resid_lev(model)
```