---
output: _output.yaml
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Agenda

<hr>

## Libraries

<hr>

```{r glm1, message=FALSE, results='hide'}
library(readr)
library(caret)
library(forcats)
library(magrittr)
library(blorr)
```


## Data

<hr>

```{r glm2, echo=TRUE, message=FALSE, results='hide'}
bank <- read_csv("data/bank.csv", col_types = list(
  col_integer(), 
  col_factor(levels = c("management", "technician", "entrepreneur", 
                        "blue-collar", "unknown", "retired", "admin.", 
                        "services", "self-employed", "unemployed", "housemaid",
                        "student")),
  col_factor(levels = c("married", "single", "divorced")),
  col_factor(levels = c("tertiary", "secondary", "unknown", "primary")),
  col_factor(levels = c("no", "yes")), col_double(),
  col_factor(levels = c("yes", "no")), col_factor(levels = c("yes", "no")),
  col_factor(levels = c("unknown", "cellular", "telephone")), col_integer(),
  col_factor(levels = c("may", "jun", "jul", "aug", "oct", "nov", "dec", "jan", 
                        "feb", "mar", "apr", "sep")), 
  col_integer(), col_integer(), col_integer(), col_integer(),
  col_factor(levels = c("unknown", "failure", "other", "success")),
  col_factor(levels = c("no", "yes"))
))
```

## Data Partition

<hr>

```{r glm3}
out <- createDataPartition(y = bank$age, p = 0.7, list = FALSE)
train <- bank[out, ]
test <- bank[-out, ]
```

## Recode Response

<hr>

```{r glm4}
bank$y <- fct_recode(bank$y, `0` = "no", `1` = "yes")
```

## Bivariate Analysis

<hr>

```{r glm5}
blr_woe_iv(bank, marital, y)
```

## Bivariate Analysis

<hr>

```{r glm6}
blr_woe_iv(bank, job, y)
```

## Bivariate Analysis

<hr>

```{r glm7}
blr_woe_iv(bank, default, y)
```

## Bivariate Analysis

<hr>

```{r glm8}
blr_bivariate_analysis(bank, y, marital)
```

## Bivariate Analysis

<hr>

```{r glm9}
blr_bivariate_analysis(bank, y, job)
```

## Regression

<hr>

```{r glm10, fig.align='center'}
model <- glm(y ~  age + duration + previous + housing + default +
               loan + poutcome + job + marital, data = bank, 
             family = binomial(link = 'logit'))
```

## Regression

<hr>

```{r glm11}
summary(model)
```

## Regression

<hr>

```{r glm12, fig.align='center'}
blr_regress(model)
```

## Model Fit Statistics

<hr>

```{r glm13, fig.align='center'}
blr_model_fit_stats(model)
```

## Confusion Matrix

<hr>

```{r glm14}
blr_confusion_matrix(model, cutoff = 0.5)
```

## Variable Selection

<hr>

```{r glm15}
blr_step_aic_forward(model)
```

## Variable Selection

<hr>

```{r glm16}
blr_step_aic_backward(model)
```


## Variable Selection

<hr>

```{r glm17}
blr_step_aic_both(model)
```


## Hosmer Lemeshow Test

<hr>

```{r glm18}
blr_test_hosmer_lemeshow(model)
```

## Gains Table

<hr>

```{r glm19, fig.align='center'}
blr_gains_table(model)
```

## Lift Chart

<hr>

```{r glm20, fig.align='center'}
model %>%
  blr_gains_table() %>%
  plot()
```

## ROC Curve

<hr>

```{r glm21, fig.align='center'}
model %>%
  blr_gains_table() %>%
  blr_roc_curve()
```

## KS Statistic

<hr>

```{r glm22, fig.align='center'}
model %>%
  blr_gains_table() %>%
  blr_ks_chart()
```

## Lorenz Curve

<hr>

```{r glm23, fig.align='center'}
blr_lorenz_curve(model)
```

## Decile Capture Rate

<hr>

```{r glm24, fig.align='center'}
model %>%
  blr_gains_table() %>%
  blr_decile_capture_rate()
```

## Decile Lift Chart

<hr>

```{r glm25, fig.align='center'}
model %>%
  blr_gains_table() %>%
  blr_decile_lift_chart()
```

